Commit Rater

### 2015-08-26 presentations/paper/threats.tex
Fix Marco's threats and remove double conclusion

Based on our two research questions, our main conclusions are:
\begin{itemize}
  \item We can recognize a ``good'' commit by a high rating from the Commit Rater since the rating reflects how much the author adhered to certain criteria
  \item Our personally chosen criteria are valid because they show statistical ralations to the criteria taken from official sources
\end{itemize}

\TODO{Revisit this section after drawing real conclusions}

@@

Furthermore, our tests for the criteria may be flawed. The prime example for such a test is the one for the spelling criterion. As already mentioned in \label{subs:no_misspelling}, spell-checking highly technical texts is very problematic and the results of this test may not be trustworthy.

>>>>

\TODO{introduce without concluding}

@@

Furthermore, our tests for the criteria may be flawed. The prime example for such a test is the one for the spelling criterion. As already mentioned in section \ref{subs:no_misspelling}, spell-checking highly technical texts is very problematic and the results of this test may not be trustworthy.
